---
title: "Descriptive Analysis for the dummy data"
author: "Nadeesri Wijekoon"
date: "July 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=F }
source("dummyData.R")
library(lme4)
library(ggplot2)
library(gridExtra)
library(grid)
data<-data[,-1]
```

Summary Statistics for data are given below
```{r warning=F}
summary(data)
```

We can see that MFS, AMT BIN_MFS and PRIOR_BIN_MFS variables have large number of missing values compared to other variables in the data set. Mean dose of Morphine is 198.4 mg and maxmimum were given is 480mg.

```{r}
interaction.plot(TIME,BIN_MFS,MFS,type = "b",data=data)
```

### Boxplots of Weights of babies by BIN_MFS. 
```{r warning=F}
library(ggplot2)
p<-ggplot(data, aes(x=BIN_MFS, y=WT)) + 
  geom_boxplot()+labs(title="Boxplot of Weights of babies by BIN_MFS")
q<-ggplot(data, aes(x=BIN_MFS, y=AMT)) + 
  geom_boxplot()+labs(title="Boxplot of AMT of babies by BIN_MFS")
grid.arrange(p,q,ncol=2,nrow=1)
```


### Dose and MFS variation with time
Removed AMT variable and BIN_MFS and PRIOR_BIN_MFS since those variables have considerable amount of missing values. 
```{r warning=F}
data.na<-data[,-c(3,5,6)]
data.na<-na.omit(data.na)
#View(data.na)
```

#### For all the patients TIME vs. MFS

```{r warning=F}
library(ggplot2)
library(gridExtra)
library(grid)
ggplot(data.na, aes(x=TIME, y=MFS, color=factor(ID))) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+geom_smooth()

store<-list()
for(i in 1:10){
  data.one<-subset(data.na,ID==i,)
  store[[i]]<-ggplot(data.one, aes(x=TIME, y=MFS)) +
    geom_line() + geom_point() +
    theme_bw()
}

title1=textGrob("TIME vs. MFS for each subject", gp=gpar(fontface="bold"))
title2=textGrob("Left side is odd numbered subjects and right side is even numbered subjects", gp=gpar(fontface="bold"))
grid.arrange(store[[1]],store[[2]],store[[3]],store[[4]],store[[5]],
             store[[6]],store[[7]],store[[8]],store[[9]],store[[10]],ncol=2,nrow=5,top=title1,
             bottom=title2)
```


#### For all the patients TIME vs. DOSE
```{r warning=F}
ggplot(data.na, aes(x=TIME, y=DOSE, color=factor(ID))) +
  geom_line() + geom_point() +
  theme_bw()

store1<-list()
for(i in 1:10){
  data.one<-subset(data.na,ID==i,)
  store1[[i]]<-ggplot(data.one, aes(x=TIME, y=DOSE)) +
    geom_line() + geom_point() +
    theme_bw()
}

title1=textGrob("TIME vs. DOSE for each subject", gp=gpar(fontface="bold"))
title2=textGrob("Left side is odd numbered subjects and right side is even numbered subjects", gp=gpar(fontface="bold"))
grid.arrange(store1[[1]],store1[[2]],store1[[3]],store1[[4]],store1[[5]],
             store1[[6]],store1[[7]],store1[[8]],store1[[9]],store1[[10]],ncol=2,nrow=5,top=title1,
             bottom=title2)

```

